\documentclass{beamer}

\usepackage{graphicx}
\usepackage{tabularx} % for tables

\title{GYM Web Project}
\author{eng: abdulwahab el mestkawy}
\date{\today}	

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Team members}
\begin{enumerate}
\item Omar Reda Mohamed
\item Mohamed Sherif Mohamed
\item Ahmed Mohamed Fawzy
\item Waleed El-Sayed Essawy
\item Khaled Mohamed Sami
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Home Page}

Welcome to our gym web project! Our goal is to provide a comprehensive and convenient platform for our members to access workout programs, meet with trainers, and track their progress.
\end{frame}

\begin{frame}
\frametitle{About Page}

Learn more about our gym and our mission to promote healthy living and personal fitness. We offer a range of services and facilities, including state-of-the-art equipment, group fitness classes, and one-on-one training sessions.
\end{frame}

\begin{frame}
\frametitle{Programs Page}

We offer a variety of programs to meet the needs and goals of our members. Our programs include:

\begin{itemize}
\item \textbf{Basic Fitness}: Working out in the gym not only helps you shed those extra pounds, keeps you fit but also has a whole health benefits.
\item \textbf{Body Building}: The set-up of this program is to perform three main exercises that target the main muscle groups in the body performing five sets of five repetitions. At the end of each workout, you can add in a few sets of isolated exercises if you like.
\item \textbf{Yoga}: Practicing yoga can feel so good that some of us fail to incorporate other forms of exercise, each with their own benefits.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Trainers Page}

Our team of trainers is dedicated to helping our members reach their fitness goals. Meet our trainers:

\begin{itemize}
\item \textbf{IVAN GUNDOGAN} - Fitness Trainer
\item \textbf{KAROLINA GRABOWSKA} - Yoga Trainer
\item \textbf{WISHFUL SHRINKING} - Strength Trainer
\item \textbf{Maria gerogo} - Fitness Trainer
\item \textbf{John deep} - Yoga Trainer
\item \textbf{Morgan Hansa} - Strength Trainer
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Plans Page}

The plans page provides information about the various membership options available at the gym, including:

\begin{itemize}
\item \textbf{Basic} - \$20/mo: This plan includes 1 month of cardio and yoga training.
\item \textbf{Standard} - \$50/mo: This plan includes 3 months of weight-lifting, cardio, and yoga training.
\item \textbf{Premium} - \$100/mo: This plan includes weight-lifting, cardio, yoga training, and protein-powder.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Dates Page}

The dates page will feature a table with the schedule of the gym's operating hours for each day of the week, from Monday to Sunday.

\begin{table}[h]
\begin{tabular}{|c|c|}
\hline
\textbf{Day} & \textbf{Hours} \\ \hline
Monday & 8:30 AM - 10:00 PM \\ \hline
Tuesday & 8:30 AM - 10:00 PM \\ \hline
Wednesday & 8:30 AM - 10:00 PM \\ \hline
Thursday & 8:30 AM - 10:00 PM \\ \hline
Friday & 8:30 AM - 10:00 PM \\ \hline
Saturday & 8:30 AM - 5:00 PM \\ \hline
Sunday & 8:30 AM - 5:00 PM \\ \hline
\end{tabular}
\caption{Operating hours for GYM}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Exercises Page}

The exercises page provides information and instructions for various exercises commonly performed at the gym, including:

\begin{itemize}
\item \textbf{Push Press}: A compound exercise targeting the shoulders, triceps, and upper back.
\item \textbf{Bench Press}: A compound exercise targeting the chest, triceps, and shoulders.
\item \textbf{Goblet squat}: A compound exercise that targets the quadriceps, glutes, and lower back.
\item \textbf{Dumble single arm}: An isolation exercise that targets the biceps.
\item \textbf{Shoulder lateral raise}: An isolation exercise that targets the shoulders.
\item \textbf{Barbell bicep curls}: An isolation exercise that targets the biceps.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Contact Page}

The contact page provides information on how to get in touch with the gym, including the address, phone number, email, and social media accounts.
\end{frame}

\begin{frame}
\frametitle{Login Page}

The login page allows registered users to access their account and view their personal information, schedules, and progress.
\end{frame}

\begin{frame}
\frametitle{Register Page}

The register page allows new users to create an account and become a member of the gym.
\end{frame}

\end{document}
